---
title: "xts basics"
output: html_notebook   
---

# xts

xTensible time series. Flexible and powerful management of time series. At the heart of each xts object: a matrix with an index, which is a date vector. That is exemplified in the xts constructor:


```{r, message=FALSE, warning=FALSE}
library(xts)
library(zoo)
x <- matrix(c(1, 2, 3, 4), nrow = 2, ncol = 2)
idx <- as.Date(c("2015-01-01", "2016-01-01"))
X <- xts(x, order.by = idx) # use unique argument if you want to enforce unique rows by index. 
X
```

## Decomposing: getting the matrix and the index out.

```{r}
index(X)
```

```{r}
coredata(X)
```

xts benefit over ts: the index can be any type of Date, as internally convertes them all to a same object.

## Converting, Importing and Exporting xts objects

### Converting

```{r}
data("sunspots")
head(as.xts(sunspots))
```

### Reading from csv file via read_csv

From a csv file and tibble:

```{r, message=FALSE, warning=FALSE}
library(readr)
library(lubridate)
datos <- read_csv("inputs2.csv")
datos$Date <- mdy(datos$Date)
xts_df = as.xts(datos[,-1], order.by = datos$Date)
head(xts_df)
```

### Read Zoo with index directly

```{r}
xts_zoo <- as.xts(read.zoo(file = "inputs2.csv", format = "%m/%d/%Y", sep = ",", header = TRUE, nrows = 222))
head(xts_zoo)
```

```{r}
write.zoo(xts_zoo, "exported_zoo.csv") #use saveRDS() if object is gonna be used later on.
```

