---
title: "Time Subsetting"
output: html_notebook
---

```{r}
library(zoo)
library(xts)
```

Note: xts represents dates with the standard ISO 8601:2004 representation: 2000-01-01.

```{r}
data(edhec, package = "PerformanceAnalytics") # load xts data
head(edhec)
```

We can get a whole year: 

```{r}
edhec["1997"]
```

Between two dates (including):

```{r}
edhec["1997-01/1998-10"]
```

From a given date onwards (including initial Date):

```{r}
edhec["2008-10/"]
```

Until a given date (including):

```{r}
edhec["/1998-01"]
```

## Other Queries

In addition to time based queries, xts objects can also be subsetted with integers for rows and columns, or with logical subsetting. 

```{r}
edhec[1 , c("Short Selling", "Funds of Funds")]
```

```{r}
edhec[index(edhec)> "2005-01-31", "Funds of Funds"] # equivalent to edhec["2005-02/", c("Funds of Funds")]
```

To get the integer based version of a Date query, use the argument which.i:

```{r}
edhec["2009-07/", which.i = TRUE]
```

Thus, you could say to take all the element that aren't in a certain date interval:

```{r}
edhec[-edhec["2000-01/2009/", which.i = TRUE]]
```

Finally, to get certain months at every year, or certain dates, use the family .index functions:

```{r}
edhec[.indexmon(edhec)== 0]

#SPY[.indexmon(SPY)==0]   # January for all years (note zero-based indexing!)
#SPY[.indexmday(SPY)==1]  # The first of every month
#SPY[.indexwday(SPY)==1]
```

